---
title: 'Tidy Tuesday #3'
author: "Michael Nadeau"
output: 
  html_document:
    df_print: paged
    code_download: true
    theme: cerulean
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, error=TRUE, message=FALSE, warning=FALSE)
```


```{r}
library(tidyverse)     # for data cleaning and plotting
library(gardenR)       # for Lisa's garden data
library(lubridate)     # for date manipulation
library(openintro)     # for the abbr2state() function
library(palmerpenguins)# for Palmer penguin data
library(maps)          # for map data
library(ggmap)         # for mapping points on maps
library(gplots)        # for col2hex() function
library(RColorBrewer)  # for color palettes
library(sf)            # for working with spatial data
library(leaflet)       # for highly customizable mapping
library(ggthemes)      # for more themes (including theme_map())
theme_set(theme_minimal())
```

```{r}
PAstations<- stations %>% 
  filter(STATE == "PA")
```

```{r, fig.alt = "Alternative Fuel Stations In Pennsylvania"}
PA <- get_stamenmap(
  bbox = c(left = -80.586, bottom = 39.550, right = -74.598, top = 42.318), 
  maptype = "toner-hybrid",
  zoom = 7)

# Plot the points on the map
ggmap(PA) + # creates the map "background"
  geom_point(data = PAstations, 
             aes(x = X, y = Y), 
             color = "purple",
             alpha = 5, 
             size = 1.1) +
  labs(title = "Alternative Fuel Stations In Pennsylvania", caption = "Created by Michael Nadeau") +
  theme_map()
```


## Instructions and tips

ake a minute to plan out on paper or the white board what you want your plot to look like and then dive into the code. And make sure to read about what the variables are first! 

When you are finished, please delete all the unneeded code and instructions and uncomment (delete the `#`) in the options section of code at the top. If you feel up for it, we encourage you to tweet out your graph with the `#TidyTuesday` hashtag and tag `@lisalendway` (Prof. Lisa) and `@Sintripetal` (Prof. Lauren). See the Tidy Tuesday description file if you want to use our `@MacTidyTuesday` Twitter account to do that. PLEASE take a moment to read the message at the top about alt text. If you want to post on Twitter, be sure to add that. If you need help, ask. Also, consider adding a caption or tag label with your name and source of the dataset. You can do this by adding something like: `labs(caption = "Plot created by YOURNAME, data from DATASOURCE")` to your plot code.

